Enter our title here

### 2017-08-08 manuscript.tex
Update manuscript.tex

With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R.

>>>>

With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R.
For students who have never been exposed to programing, the \textit{R} interface can be a intimidating. It is often the case
that the main source of student difficulties are with software and not the statistical concepts themselves (Hare2017). To 
overcome this learning curve, instructors utilize R teaching tools such as Swirl and TryR. Swirl is sim
